GLMM

### 2023-10-26 Code/GLMM.Rmd
Removed a few summaries of stuff that wasn't needed
Changed the data source file as I renamed it
Fixed line width
added more comments

```{r}
summary(with2022_heat_gamma_log)
```

@@

This next chunk of code runs the simulation code for each dataset comparing the
two effect model to the base model
```{r}
#7
set.seed(1)
sim_two_effect_time(without2022_two_effect_gamma_log, without2022_one_gamma_log, 0.1)
sim_two_effect_time(with2022_two_effect_gamma_log, with2022_one_gamma_log, 0.1)
```

@@

>>>>

```{r}
summary(with2022_heat_gamma_log)
summary(without2022_heat_gamma_log)
```

@@

This next chunk of code runs the simulation code for each dataset comparing the
two effect model to the base model. We run this code at 3 reaction time barriers:
0.08, 0.09, and 0.1 seconds.
```{r}
#7
set.seed(1)
sim_two_effect_time(without2022_two_effect_gamma_log,
                    without2022_one_gamma_log, 0.1)
sim_two_effect_time(with2022_two_effect_gamma_log,
                    with2022_one_gamma_log, 0.1)
```

@@

women_finals <- subset(times, Type == "F" & Gender == "F" & Time != 'DQ') # & Year < 2022)
women_pooled <- subset(times, (Type == "F" | Type == "S") & Gender == "F" & Time != 'DQ')
